---
title: "Lab 7 Rank-Based Test"
author: "Nakoa Farrant"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi this is Nakoa and I am your creator!

Collaborators (it's rachel and I'm a collaborator)

```{r}

library(tidyverse)
kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram() +
  facet_wrap(~Gender)

```


ahh shh push it:


Is there a significant difference in pre-talk hermit scores for females and males? 

Unpaired: Mann-Whitney U (wilcox.test unpaired)
```{r}
mwu_kermit = kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)
mwu_kermit
```
... there is no significant difference between gender in pre-talk hermit scores. 


Nak attack is back:

Is there a significant difference in Kermit ranks for pre-talk and post-talk scores (ignoring all other variables)?

H0: No significant difference

```{r}
wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE) 
# only makes sense to consider data paired for pre and post opinion of same individual

wsr_kermit
```
Retain the null hypothesis that there is no significant difference in Kermit rankings before and after his talk (statistical summary...)







